\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-02 manuscript.Rmd
Discussion updates

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one, making it a 5 point Likert type response format. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]. We confirmed the latent structure obtained in the EFA by conducting a categorical "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV). We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework. To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].Also the readability index was analyzed using "Flesch-Kincaid Grade Level" [@flesch1948new].  Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.

@@

## Semantic Analysis and Readability
To find out if our developed tool (23 items) is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy. LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51. Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age abobe 8.33.

>>>>

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one, making it a 5 point Likert type response format. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]. We confirmed the latent structure obtained in the EFA by conducting a categorical "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV). We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework. To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].  Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.

@@

## Semantic Analysis 
To find out if our developed tool (23 items) is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy. LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51. Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age abobe 8.33.
